The Effects of the NBA COVID Bubble on the NBA Playoffs

### 2020-11-12 Manuscript/NBABubbleAnalysis.Rmd
Update NBABubbleAnalysis.Rmd

Away teams saw more of an impact than home teams. For starters, there is a
significant increase in mean points per game, indicated by p-value of 0.0008 for z-test and
0.0004 for Wilcoxon. It is important to note both p-values also remain significant after
a Bonferonni correction giving strong indication of significance. The average difference in points is estimated to 
be about 5 points (95% CI: 2.083, 7.988).Likewise, the away team two point
shooting efficiency increased significantly based on p-value of 0.0003
for both the z-test and Wilcoxon test. Again both p-values remain signficant after Bonferroni correction.
The average difference can be estimated to be about 0.03 (95% CI: 0.015, 0.050). However,
unlike two point shooting, away teams did not see a statistically significant difference in three point and free
throw shooting. Overall, away teams have evidence of change in performance in
the bubble. The away teams seemed to perform better than they would under normal
conditions as a visiting team.

>>>>

Away teams saw more of an impact than home teams. For starters, there is a
significant increase in mean points per game, indicated by p-value of 0.0008 for z-test and
0.0004 for Wilcoxon. It is important to note both p-values also remain significant after
a Bonferonni correction giving strong indication of significance. The average difference in points is estimated to 
be about 5 points (95% CI: 2.083, 7.988). Likewise, the away team two point
shooting efficiency increased significantly based on p-value of 0.0003
for both the z-test and Wilcoxon test. Again, both p-values remain signficant after Bonferroni correction.
The average difference can be estimated to be about 0.03 (95% CI: 0.015, 0.050). However,
unlike two-point shooting, away teams did not see a statistically significant difference in three-point and free
throw shooting. Overall, away teams have evidence of change in performance in
the bubble. The away teams seemed to perform better than they would under normal
conditions as a visiting team.
